
### Load libraries  
```{r, Libraries, include = FALSE}
rm(list=ls())

# Load Required Packages
all_installed_packaged <- installed.packages()[, "Package"]
# Install any missing, but required packages
if (!"dplyr" %in% all_installed_packaged) {
  install.packages("dplyr")
}

if (!"tidyverse" %in% all_installed_packaged) {
  install.packages("tidyverse")
}

if (!"ggplot2" %in% all_installed_packaged) {
  install.packages("ggplot2")
}

if (!"effsize" %in% all_installed_packaged) {
  install.packages("effsize")
}

if (!"" %in% all_installed_packaged) {
  install.packages("")
}


library(dplyr)
library(tidyverse)
library(ggplot2)
library(effsize)
```

### Load selftest data
```{r}
# Load data
combined_data_selftest <- read.csv("Combined_dataset_selftest_final.csv")
final_data_selftest <- read.csv("full_dataset_selftest_final.csv")

# Rename proportion to mean
final_data_selftest <- final_data_selftest %>%
  dplyr::rename(mean = Percentage.infected)

# Remove X column 
combined_data_selftest <- combined_data_selftest[,-1]

# Rename variables as factors for final data
final_data_selftest$Network.size <- as.factor(final_data_selftest$Network.size) 
final_data_selftest$Bubble.size <- as.factor(final_data_selftest$Bubble.size) 
final_data_selftest$PCR.frequency <- as.factor(final_data_selftest$PCR.frequency) 
final_data_selftest$R <- as.factor(final_data_selftest$R)

# Rename variables as factors for combined data
combined_data_selftest$Network.size <- as.factor(combined_data_selftest$Network.size) 
combined_data_selftest$Bubble.size <- as.factor(combined_data_selftest$Bubble.size) 
combined_data_selftest$PCR.frequency <- as.factor(combined_data_selftest$PCR.frequency) 
combined_data_selftest$R <- as.factor(combined_data_selftest$R)

# Make a proportion out of percentage infected for final data
final_data_selftest$mean <- (final_data_selftest$mean/100)

# Rename percentage infected to proportion infected
final_data_selftest <- final_data_selftest %>%
  dplyr::rename(Proportion.infected = mean)

#Rename Semiweekly
final_data_selftest$PCR.frequency <- gsub("semiweekly", "semi-weekly", final_data_selftest$PCR.frequency)
combined_data_selftest$PCR.frequency <- gsub("semiweekly", "semi-weekly", combined_data_selftest$PCR.frequency)

# Do the same for the sd of final data
final_data_selftest$sd <- (final_data_selftest$sd/100)

# Round Means for final data
final_data_selftest$Proportion.infected <- round(final_data_selftest$Proportion.infected, 2)

# Round Means for combined data
combined_data_selftest$Percentage.infected <- round(combined_data_selftest$Percentage.infected, 2)

# Check if succeeded
final_data_selftest
combined_data_selftest
```

### Create function to make table of effectsizes (Cohens' D)  
```{r}
Effectsize <- function(Network.size, R){

# Creating data frame to store values in
effectsize.table <- data.frame(Network_size = NA, Bubble_size = NA, PCR_frequency = NA, R = NA, Effect_size = NA,
                               Magnitude = NA)


# Specifying parameters for the for loop
Network.size = c(Network.size)
Bubble.size = c(5, 10, 25, 50, 'none')
PCR.frequency = c("none", "workday", "semi-weekly", "weekly", "monthly")
R = c(R)



for (i in 1:length(Network.size)) {
  for (j in 1:length(Bubble.size)) {
    for (k in 1:length(PCR.frequency)) {
      for (l in 1:length(R)) {
        

        w <- Network.size[i]
        x <- Bubble.size[j]
        y <- PCR.frequency[k]
        z <- R[l]
        
                
        # Get values of control condition 
        control <- combined_data_selftest %>% 
          filter(Network.size == w & PCR.frequency == "none" & Bubble.size == "none" & R == z)
        
        # store them
        control <- control$Percentage.infected
        
        
        # Get values of treatment condition
        treatment <- combined_data_selftest %>%
        filter(Network.size == w & Bubble.size == x & PCR.frequency == y & R == z)

        # store them
        treatment <- treatment$Percentage.infected
        
        # Calculate Cohens' D  
        Effect_size = cohen.d(control, treatment)
        
        # Set all variables in data frame
        x <- data.frame(Network_size = Network.size[i], Bubble_size = Bubble.size[j], PCR_frequency = PCR.frequency[k],
                        R = R[l], Effect_size = Effect_size$estimate, Magnitude = Effect_size$magnitude)
        
        # Store it in combined data frame
        effectsize.table <- rbind(effectsize.table, x)
        }
      }
    }
  }
        # Show data frame without the NA row
        effectsize.table <- na.omit(effectsize.table)
        
        # Round effectsize to 2 decimals
        effectsize.table$Effect_size <- round(effectsize.table$Effect_size, 2)
        
        # Return effect size table
        print(effectsize.table)

}

```


### Loop to create effectsize table for self administered data 
```{r}
# Specify parameters
Network.size = c(20, 50, 100, 250)
R = c(1, 1.5, 2, 2.5)

# Loop
for (i in 1:length(Network.size)) {
  for (j in 1:length(R)) {
    Effectsize(Network.size = Network.size[i], R = R[j])
  }
}

```


### hypothesis:
##  What is the impact of self administered testing the transmission of COVID-19 in the workplace?
#   Does the frequency of testing matter (Refer to effectsizes)
```{r}
# Fitting the model
mod <- glm(Proportion.infected ~ PCR.frequency, final_data_selftest, family = binomial(link = "logit"))


# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```

#  Calculate Pseudo R2 for every network size and put data in a table
#  plot the table
```{r}
# Values of Network size
unique(final_data_selftest$Network.size)

# Create empty table
table <- data.frame(Network_size = NA, Pseudo_R2 = NA)

# Implement here
Network_size = c(20, 50, 100, 250)

# Create loop to calculate psuedo R2 for every netsize
for (i in 1:length(Network_size)) {
  test <- final_data_selftest %>% filter(Network.size == Network_size[i])

  # Fitting the model
  mod <- glm(Proportion.infected ~ PCR.frequency, test, family = binomial(link = "logit"))

  # Calculate Pseudo R2 for the model
  pR2 = 1 - mod$deviance / mod$null.devianc
  # Return value
  print(pR2)
  
  
  # Set all variables in data frame
  x <- data.frame(Network_size = Network.size[i], Pseudo_R2 = pR2)
        
  # Store it in combined data frame
  table <- rbind(table, x)
}
# Omit NA's
table <- na.omit(table)
table
```

# Load administered test data
```{r}
Combined_dataset_administered_test <- read.csv("Combined_dataset_administered_test_final.csv")
Full_dataset_administered_test <- read.csv("full_dataset_administered_test_final.csv")


Full_dataset_administered_test <- Full_dataset_administered_test %>%
  dplyr::rename(mean = Percentage.infected)


# Remove X column 
Combined_dataset_administered_test <- Combined_dataset_administered_test[,-1]

# Rename variables as factors for final data
Full_dataset_administered_test$Network.size <- as.factor(Full_dataset_administered_test$Network.size) 
Full_dataset_administered_test$Bubble.size <- as.factor(Full_dataset_administered_test$Bubble.size) 
Full_dataset_administered_test$PCR.frequency <- as.factor(Full_dataset_administered_test$PCR.frequency) 
Full_dataset_administered_test$R <- as.factor(Full_dataset_administered_test$R)

# Rename variables as factors for combined data
Combined_dataset_administered_test$Network.size <- as.factor(Combined_dataset_administered_test$Network.size) 
Combined_dataset_administered_test$Bubble.size <- as.factor(Combined_dataset_administered_test$Bubble.size) 
Combined_dataset_administered_test$PCR.frequency <- as.factor(Combined_dataset_administered_test$PCR.frequency) 
Combined_dataset_administered_test$R <- as.factor(Combined_dataset_administered_test$R)

# Make a proportion out of percentage infected for final data
Full_dataset_administered_test$mean <- (Full_dataset_administered_test$mean/100)

# Rename percentage infected to proportion infected
Full_dataset_administered_test <- Full_dataset_administered_test %>%
  dplyr::rename(Proportion.infected = mean)

#Rename Semiweekly
Full_dataset_administered_test$PCR.frequency <- gsub("semiweekly", "semi-weekly",
                                                     Full_dataset_administered_test$PCR.frequency)
Combined_dataset_administered_test$PCR.frequency <- gsub("semiweekly", "semi-weekly",
                                                         Combined_dataset_administered_test$PCR.frequency)

# Do the same for the sd of final data
Full_dataset_administered_test$sd <- (Full_dataset_administered_test$sd/100)

# Round Means for final data
Full_dataset_administered_test$Proportion.infected <- round(Full_dataset_administered_test$Proportion.infected, 2)

# Round Means for combined data
Combined_dataset_administered_test$Percentage.infected <- round(Combined_dataset_administered_test$Percentage.infected, 2)

# Check if succeeded
Full_dataset_administered_test
Combined_dataset_administered_test
```

### Create function to make table of effectsizes (Cohens' D)  
```{r}
Effectsize <- function(Network.size, R){

# Creating data frame to store values in
effectsize.table <- data.frame(Network_size = NA, Bubble_size = NA, PCR_frequency = NA, R = NA, Effect_size = NA,
                               Magnitude = NA)


# Specifying parameters for the for loop
Network.size = c(Network.size)
Bubble.size = c(5, 10, 25, 50, 'none')
PCR.frequency = c("none", "workday", "semi-weekly", "weekly", "monthly")
R = c(R)



for (i in 1:length(Network.size)) {
  for (j in 1:length(Bubble.size)) {
    for (k in 1:length(PCR.frequency)) {
      for (l in 1:length(R)) {
        

        w <- Network.size[i]
        x <- Bubble.size[j]
        y <- PCR.frequency[k]
        z <- R[l]
        
                
        # Get values of control condition 
        control <- Combined_dataset_administered_test %>% 
          filter(Network.size == w & PCR.frequency == "none" & Bubble.size == "none" & R == z)
        
        # store them
        control <- control$Percentage.infected
        
        
        # Get values of treatment condition
        treatment <- Combined_dataset_administered_test %>%
        filter(Network.size == w & Bubble.size == x & PCR.frequency == y & R == z)

        # store them
        treatment <- treatment$Percentage.infected
        
        # Calculate Cohens' D  
        Effect_size = cohen.d(control, treatment)
        
        # Set all variables in data frame
        x <- data.frame(Network_size = Network.size[i], Bubble_size = Bubble.size[j], PCR_frequency = PCR.frequency[k],
                        R = R[l], Effect_size = Effect_size$estimate, Magnitude = Effect_size$magnitude)
        
        # Store it in combined data frame
        effectsize.table <- rbind(effectsize.table, x)
        }
      }
    }
  }
        # Show data frame without the NA row
        effectsize.table <- na.omit(effectsize.table)
        
        # Round effectsize to 2 decimals
        effectsize.table$Effect_size <- round(effectsize.table$Effect_size, 2)
        
        # Return effect size table
        print(effectsize.table)

}

```

### Loop to create effectsize table for administered test data 
```{r}
# Specify parameters
Network.size = c(20, 50, 100, 250)
R = c(1, 1.5, 2, 2.5)

# Loop
for (i in 1:length(Network.size)) {
  for (j in 1:length(R)) {
    Effectsize(Network.size = Network.size[i], R = R[j])
  }
}

```

### hypothesis:
##  What is the impact of administered test data on the transmission of COVID-19 in the workplace?
#   Does the frequency of testing matter (Refer to effectsizes)
```{r}
# Fitting the model
mod <- glm(Proportion.infected ~ PCR.frequency, Full_dataset_administered_test, family = binomial(link = "logit"))


# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```


#  Calculate Pseudo R2 for every network size and put data in a table
#  plot the table
```{r}
# Values of Network size
unique(Full_dataset_administered_test$Network.size)

# Create empty table
table <- data.frame(Network_size = NA, Pseudo_R2 = NA)

# Implement here
Network_size = c(20, 50, 100, 250)

# Create loop to calculate psuedo R2 for every netsize
for (i in 1:length(Network_size)) {
  test <- Full_dataset_administered_test %>% filter(Network.size == Network_size[i])

  # Fitting the model
  mod <- glm(Proportion.infected ~ PCR.frequency, test, family = binomial(link = "logit"))

  # Calculate Pseudo R2 for the model
  pR2 = 1 - mod$deviance / mod$null.devianc
  # Return value
  print(pR2)
  
  
  # Set all variables in data frame
  x <- data.frame(Network_size = Network.size[i], Pseudo_R2 = pR2)
        
  # Store it in combined data frame
  table <- rbind(table, x)
}
# Omit NA's
table <- na.omit(table)
table
```


# Plot 
```{r, fig.height=6, fig.width=12}
# Add column to differntiate between tests
final_data_selftest$test <- 'self-administered'
Full_dataset_administered_test$test <- 'expert-administered'

# join dataframes
combined_data <- rbind(final_data_selftest, Full_dataset_administered_test)
# Set PCR frequency is right order for plot
combined_data$PCR.frequency <- factor(combined_data$PCR.frequency, 
                                      levels=c("workday", "semi-weekly", "weekly", "monthly"))

combined_data <- combined_data %>% filter(PCR.frequency != "none")

ggplot(combined_data, aes(x = Network.size, y = Proportion.infected, fill = factor(test))) +
  stat_boxplot(geom ='errorbar') +
  geom_boxplot() +
  facet_wrap(vars(PCR.frequency), ncol = 5) +
  labs(fill='Method of administration') +
  theme(legend.position="top") +
  scale_fill_manual(values = c("#99B898", "#FECEA8")) +
  theme_bw() +
  stat_summary(fun.y=mean, geom="point", aes(group=test), position=position_dodge(.9), 
                size=2) +
  labs(x = 'Network size', y = 'Proportion infected')
  

```















