
### Load libraries  
```{r, Libraries, include = FALSE}
rm(list=ls())

# Load Required Packages
all_installed_packaged <- installed.packages()[, "Package"]
# Install any missing, but required packages
if (!"dplyr" %in% all_installed_packaged) {
  install.packages("dplyr")
}

if (!"tidyverse" %in% all_installed_packaged) {
  install.packages("tidyverse")
}

if (!"ggplot2" %in% all_installed_packaged) {
  install.packages("ggplot2")
}

if (!"effsize" %in% all_installed_packaged) {
  install.packages("effsize")
}

if (!"" %in% all_installed_packaged) {
  install.packages("")
}


library(dplyr)
library(tidyverse)
library(ggplot2)
library(effsize)
```

### Prepare the datasets  
```{r}
final_data <- read.csv('Full_Dataset_thesis_final.csv')
combined_data <- read.csv('Combined_Dataset_thesis_final.csv')


# Remove X column for combined_data
combined_data <- combined_data[,-1]

# Rename variables as factors for final data
final_data$Network.size <- as.factor(final_data$Network.size) 
final_data$Bubble.size <- as.factor(final_data$Bubble.size) 
final_data$PCR.frequency <- as.factor(final_data$PCR.frequency) 
final_data$R <- as.factor(final_data$R)

# Rename variables as factors for combined data
combined_data$Network.size <- as.factor(combined_data$Network.size) 
combined_data$Bubble.size <- as.factor(combined_data$Bubble.size) 
combined_data$PCR.frequency <- as.factor(combined_data$PCR.frequency) 
combined_data$R <- as.factor(combined_data$R)

# Make a proportion out of percentage infected for final data
final_data$Percentage.infected <- (final_data$Percentage.infected/100)

# Rename percentage infected to proportion infected
final_data <- final_data %>%
  dplyr::rename(Proportion.infected = Percentage.infected)

# Do the same for the sd of final data
final_data$sd <- (final_data$sd/100)

# Round Means for final data
final_data$Proportion.infected <- round(final_data$Proportion.infected, 2)

# Round Means for combined data
combined_data$Percentage.infected <- round(combined_data$Percentage.infected, 2)

# Check if succeeded
final_data
combined_data
```


### Visual inspection of the data  
#   Plot distributions  
```{r}
# create lists for all unique values of Network size & R
x <- unique(final_data$Network.size)
y <- unique(final_data$R)

# Loop to get barcharts for every combination of Network size & R
for (i in 1:length(x)){
  for (j in 1:length(y)) {
    plot_data = final_data %>%
      filter(Network.size == x[i] & R == y[j]) 
  
  # Order Bubble size & PCR frequency in a logical way    
  plot_data$Bubble.size <- factor(plot_data$Bubble.size, levels=c("5", "10", "25", "50", "none"))
  plot_data$PCR.frequency <- factor(plot_data$PCR.frequency, levels = c("workday", "semi-weekly", "weekly", "monthly",
                                                                        "none"))

  # Make the plot
  plot = ggplot(plot_data, aes(x = Bubble.size, y = Proportion.infected, fill = PCR.frequency)) +
  geom_bar(stat = 'identity', position = position_dodge(), color="black") +
  geom_errorbar(aes(ymin=Proportion.infected, ymax=Proportion.infected+sd), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values = c("#fff5a5", "#ffaa64", "#ff8264", "#c25e00", "#B31D1D")) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggtitle(paste('Network size = ', x[i], '&', 'R =', y[j])) +
  labs(y = "Proportion infected", x = 'Bubble size') +
  guides(fill=guide_legend(title="PCR frequency")) +
  theme(legend.position="top") 

  print(plot)
  }
}
```


### Create function to make table of effectsizes (Cohens' D)  
```{r}
Effectsize <- function(Network.size, R){

# Creating data frame to store values in
effectsize.table <- data.frame(Network_size = NA, Bubble_size = NA, PCR_frequency = NA, R = NA, Effect_size = NA,
                               Magnitude = NA)


# Specifying parameters for the for loop
Network.size = c(Network.size)
Bubble.size = c(5, 10, 25, 50, 'none')
PCR.frequency = c("none", "workday", "semi-weekly", "weekly", "monthly")
R = c(R)



for (i in 1:length(Network.size)) {
  for (j in 1:length(Bubble.size)) {
    for (k in 1:length(PCR.frequency)) {
      for (l in 1:length(R)) {
        

        w <- Network.size[i]
        x <- Bubble.size[j]
        y <- PCR.frequency[k]
        z <- R[l]
        
                
        # Get values of control condition 
        control <- combined_data %>% 
          filter(Network.size == w & PCR.frequency == "none" & Bubble.size == "none" & R == z)
        
        # store them
        control <- control$Percentage.infected
        
        
        # Get values of treatment condition
        treatment <- combined_data %>%
        filter(Network.size == w & Bubble.size == x & PCR.frequency == y & R == z)

        # store them
        treatment <- treatment$Percentage.infected
        
        # Calculate Cohens' D  
        Effect_size = cohen.d(control, treatment)
        
        # Set all variables in data frame
        x <- data.frame(Network_size = Network.size[i], Bubble_size = Bubble.size[j], PCR_frequency = PCR.frequency[k],
                        R = R[l], Effect_size = Effect_size$estimate, Magnitude = Effect_size$magnitude)
        
        # Store it in combined data frame
        effectsize.table <- rbind(effectsize.table, x)
        }
      }
    }
  }
        # Show data frame without the NA row
        effectsize.table <- na.omit(effectsize.table)
        
        # Round effectsize to 2 decimals
        effectsize.table$Effect_size <- round(effectsize.table$Effect_size, 2)
        
        # Return effect size table
        print(effectsize.table)

}

```


### Loop to create effectsize table for every combination of Network size & R  
```{r}
# Specify parameters
Network.size = c(20, 50, 100, 250, 500, 1000)
R = c(1, 1.5, 2, 2.5, 3)

# Loop
for (i in 1:length(Network.size)) {
  for (j in 1:length(R)) {
    Effectsize(Network.size = Network.size[i], R = R[j])
  }
}

```


### Fit Full model  
```{r}
# Fitting the model
mod <- glm(Proportion.infected ~ Network.size  + Bubble.size + PCR.frequency + R, final_data,
           family = binomial(link = "logit"))

# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```




### Main hypothesis:  
##  What is the impact of combining contact network interventions on the transmission of COVID-19 in the workplace?  
```{r}
# Fitting the model with interaction
mod <- glm(Proportion.infected ~ Bubble.size + PCR.frequency + Bubble.size*PCR.frequency, final_data,
           family = binomial(link = "logit"))

# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```   

```{r}
# Fitting the model without interaction
mod <- glm(Proportion.infected ~ Bubble.size + PCR.frequency, final_data, family = binomial(link = "logit"))


# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```



### Plot for impact of combining interventions  
```{r}
data <- final_data %>%
  group_by(Network.size, PCR.frequency, Bubble.size) %>%
  dplyr::summarize(Mean = mean(Proportion.infected, na.rm=TRUE)) 

# Order factors
data$PCR.frequency <- factor(data$PCR.frequency, levels = c("workday", "semi-weekly", "weekly", "monthly",
                                                                        "none"))
data$Bubble.size <- factor(data$Bubble.size, levels = c("5", "10", "25", "50", "none"))
# Create plot
ggplot(data, aes(x = Bubble.size, y = Mean, fill = PCR.frequency)) +
  stat_boxplot(geom ='errorbar') + 
  geom_boxplot() +
  theme_bw() +
  theme(legend.position="top", legend.title = element_text(size = 12),
        legend.text = element_text(size = 12)) +
  scale_fill_manual(values = c("#fff5a5", "#ffaa64", "#ff8264", "#c25e00", "#B31D1D")) +
  labs(x = 'Bubble size', y = 'Proportion infected') +
  labs(fill = 'PCR frequency') 
```



### Subhypothesis 1:  
##  What is the impact of creating bubbles in the contact network on the transmission of COVID-19 in the workplace?  
```{r}
# Fitting the model
mod <- glm(Proportion.infected ~ Bubble.size, final_data, family = binomial(link = "logit"))


# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```

## Does the size of the bubble impact the effect of the intervention?
```{r, fig.height=18, fig.width=28}
data = combined_data %>% filter(PCR.frequency == 'none') %>%
  group_by(Network.size, Bubble.size, PCR.frequency, R)

# Make a proportion out of percentage infected for final data
data$Percentage.infected <- (data$Percentage.infected/100)

# Rename percentage infected to proportion infected
data <- data %>%
  dplyr::rename(Proportion.infected = Percentage.infected)

# Set Bubble size in right order for the plot
data$Bubble.size <- factor(data$Bubble.size, levels=c("5", "10", "25", "50", "none"))


# Create plot
ggplot(data=data, aes(x = Network.size, y = Proportion.infected, fill = Bubble.size)) +
  stat_boxplot(geom ='errorbar', size = 1, position=position_dodge(.9)) + 
  geom_boxplot(size = 1, position=position_dodge(.9)) +
  theme_bw() +
  labs(x = 'Network size', y = 'Proportion infected') + 
  theme(legend.position="top", legend.title = element_text(size = 35),
        legend.text = element_text(size = 35), axis.text=element_text(size=25),
        axis.title=element_text(size=20), strip.text = element_text(size=30),
        axis.title.x = element_text(size = 35), axis.title.y = element_text(size = 35)) +
  facet_wrap(vars(R), ncol=3, labeller = labeller(R = 
    c("1" = "R0 = 1",
      "1.5" = "R0 = 1.5",
      "2" = "R0 = 2",
      "2.5" = "R0 = 2.5",
      "3" = "R0 = 3"))) +
  labs(x = 'Network size', y = 'Proportion infected') +
  labs(fill= "Bubble size") +
  stat_summary(fun=mean, geom="point", size=4, position=position_dodge(.9))

```


## Does the size of the network impact the effect of the intervention?
```{r}
# Fitting the model with interaction
mod <- glm(Proportion.infected ~ Bubble.size + Network.size + Bubble.size*Network.size, final_data,
           family = binomial(link = "logit"))


# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```


```{r}
# Fitting the model without interaction
mod <- glm(Proportion.infected ~ Bubble.size + Network.size, final_data, family = binomial(link = "logit"))

# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```


#  Calculate Pseudo R2 for every network size and put data in a table
#  plot the table
```{r}
# Values of Network size
unique(final_data$Network.size)

# Create empty table
table <- data.frame(Network_size = NA, Pseudo_R2 = NA)

# Implement here
Network_size = c(20, 50, 100, 250, 500, 1000)

# Create loop to calculate psuedo R2 for every netsize
for (i in 1:length(Network_size)) {
  test <- final_data %>% filter(Network.size == Network_size[i])

  # Fitting the model
  mod <- glm(Proportion.infected ~ Bubble.size, test, family = binomial(link = "logit"))

  # Calculate Pseudo R2 for the model
  pR2 = 1 - mod$deviance / mod$null.devianc
  # Return value
  print(pR2)
  
  
  # Set all variables in data frame
  x <- data.frame(Network_size = Network_size[i], Pseudo_R2 = pR2)
        
  # Store it in combined data frame
  table <- rbind(table, x)
}
# Omit NA's
table <- na.omit(table)
table
```




### Subhypothesis 2:
##  What is the impact of PCR-testing on the transmission of COVID-19 in the workplace?
#   Does the frequency of testing matter (Refer to effectsizes)
```{r}
# Fitting the model
mod <- glm(Proportion.infected ~ PCR.frequency, final_data, family = binomial(link = "logit"))


# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```
# Calculate percentage reduction to compare with Chin et al. (2020)
# Averaged over all R's
```{r}
data <- final_data %>%
  filter(Bubble.size == 'none') %>%
    group_by(PCR.frequency) %>%
    dplyr::summarize(Mean = mean(Proportion.infected, na.rm=TRUE),
                                 sd = sd(Proportion.infected))

data %>%
  mutate(difference = (Mean/0.619333))

1-.93756
1-.73989
1-.60226
1-.48385
```

# Calculate percentage reduction to compare with Chin et al. (2020)
# R is 2.5
```{r}
data <- final_data %>%
  filter(Bubble.size == 'none' &  R == 2.5) %>%
    group_by(PCR.frequency) %>%
    dplyr::summarize(Mean = mean(Proportion.infected, na.rm=TRUE))

data %>%
  mutate(difference = (Mean/0.7683333))

1- .9154
1- .7635
1- .6001
1- .4577
```


# Create plot PCR frequency  
```{r, fig.height=18, fig.width=28}
data = combined_data %>% filter(Bubble.size == 'none') %>%
  group_by(Network.size, Bubble.size, PCR.frequency, R)

# Make a proportion out of percentage infected for final data
data$Percentage.infected <- (data$Percentage.infected/100)

# Rename percentage infected to proportion infected
data <- data %>%
  dplyr::rename(Proportion.infected = Percentage.infected)


# Set PCR frequency is right order for plot
data$PCR.frequency <- factor(data$PCR.frequency, levels = c("workday", "semi-weekly", "weekly", "monthly",
                                                                        "none"))

# Create plot
ggplot(data=data, aes(x = Network.size, y = Proportion.infected, fill = PCR.frequency)) +
  stat_boxplot(geom ='errorbar', size = 1, position=position_dodge(.9)) + 
  geom_boxplot(size = 1, position=position_dodge(.9)) +
  theme_bw() +
  labs(x = 'Network size', y = 'Proportion infected') + 
  theme(legend.position="top", legend.title = element_text(size = 35),
        legend.text = element_text(size = 35), axis.text=element_text(size=25),
        axis.title=element_text(size=20), strip.text = element_text(size=30),
        axis.title.x = element_text(size = 35), axis.title.y = element_text(size = 35)) +
  facet_wrap(vars(R), ncol=3, labeller = labeller(R = 
    c("1" = "R0 = 1",
      "1.5" = "R0 = 1.5",
      "2" = "R0 = 2",
      "2.5" = "R0 = 2.5",
      "3" = "R0 = 3"))) +
  labs(fill ='PCR frequency') +
  stat_summary(fun=mean, geom="point", size=4, position=position_dodge(.9))
```


## Does the size of the network impact the effect of the intervention?
```{r}
# Fitting the model with interaction
mod <- glm(Proportion.infected ~ PCR.frequency + Network.size + PCR.frequency*Network.size, final_data,
           family = binomial(link = "logit"))


# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```

```{r}
# Fitting the model without interaction
mod <- glm(Proportion.infected ~ PCR.frequency + Network.size, final_data, family = binomial(link = "logit"))

# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```


#  Calculate Pseudo R2 for every network size and put data in a table
#  plot the table
```{r}
# Values of Network size
unique(final_data$Network.size)

# Create empty table
table <- data.frame(Network_size = NA, Pseudo_R2 = NA)

# Implement here
Network_size = c(20, 50, 100, 250, 500, 1000)

# Create loop to calculate psuedo R2 for every netsize
for (i in 1:length(Network_size)) {
  test <- final_data %>% filter(Network.size == Network_size[i])

  # Fitting the model
  mod <- glm(Proportion.infected ~ PCR.frequency, test, family = binomial(link = "logit"))

  # Calculate Pseudo R2 for the model
  pR2 = 1 - mod$deviance / mod$null.devianc
  # Return value
  print(pR2)
  
  
  # Set all variables in data frame
  x <- data.frame(Network_size = Network_size[i], Pseudo_R2 = pR2)
        
  # Store it in combined data frame
  table <- rbind(table, x)
}
# Omit NA's
table <- na.omit(table)
table
```


 
### Subhypothesis 3:  
##   How do different effective R’s (which can encode other measures such as wearing face masks) change these impacts?  
##   Effect sizes  
```{r}
# Fitting the model
mod <- glm(Proportion.infected ~ R, final_data, family = binomial(link = "logit"))

# Calculate Pseudo R2 for the model
pR2 = 1 - mod$deviance / mod$null.devianc
pR2
```



#  Calculate Pseudo R2 of Bubble size for every R and put data in a table  
#  plot the table  
```{r}
# Values of Network size
unique(final_data$Network.size)

# Create empty table
table <- data.frame(R = NA, Pseudo_R2 = NA)

# Implement here
R = c(1, 1.5, 2, 2.5, 3)

# Create loop to calculate psuedo R2 for every netsize
for (i in 1:length(R)) {
  test <- final_data %>% filter(R == R[i])

  # Fitting the model
  mod <- glm(Proportion.infected ~ Bubble.size, test, family = binomial(link = "logit"))

  # Calculate Pseudo R2 for the model
  pR2 = 1 - mod$deviance / mod$null.devianc
  # Return value
  print(pR2)
  
  
  # Set all variables in data frame
  x <- data.frame(R = R[i], Pseudo_R2 = pR2)
        
  # Store it in combined data frame
  table <- rbind(table, x)
}
# Omit NA's
table <- na.omit(table)
table
```


# Calculate Pseudo R2 of PCR frequency for every R and put data in a table  
# plot the table  
```{r}
# Values of Network size
unique(final_data$Network.size)

# Create empty table
table <- data.frame(R = NA, Pseudo_R2 = NA)

# Implement here
R = c(1, 1.5, 2, 2.5, 3)

# Create loop to calculate psuedo R2 for every netsize
for (i in 1:length(R)) {
  test <- final_data %>% filter(R == R[i])

  # Fitting the model
  mod <- glm(Proportion.infected ~ PCR.frequency, test, family = binomial(link = "logit"))

  # Calculate Pseudo R2 for the model
  pR2 = 1 - mod$deviance / mod$null.devianc
  # Return value
  print(pR2)
  
  
  # Set all variables in data frame
  x <- data.frame(R = R[i], Pseudo_R2 = pR2)
        
  # Store it in combined data frame
  table <- rbind(table, x)
}
# Omit NA's
table <- na.omit(table)
table
```


# Chunk to get a complete dataframe of all Effect sizes, when PCR frequency = none, and plot these  
```{r, fig.height=6, fig.width=12}
data <- combined_data %>%
  filter(PCR.frequency == 'none' & Bubble.size == 'none') %>%
  group_by(Network.size, Bubble.size, PCR.frequency, R) 


data$Percentage.infected <- (data$Percentage.infected/100)

ggplot(data, aes(x = Network.size, y = Percentage.infected, fill = Network.size)) +
  stat_boxplot(geom ='errorbar') + 
  geom_boxplot() +
  facet_grid(~R, labeller = labeller(R = 
    c("1" = "R0 = 1",
      "1.5" = "R0 = 1.5",
      "2" = "R0 = 2",
      "2.5" = "R0 = 2.5",
      "3" = "R0 = 3"))) +
  theme_bw() +
  theme(legend.position="top", legend.title = element_text(size = 15),
        legend.text = element_text(size = 15), axis.text=element_text(size=10),
        axis.title=element_text(size=15), strip.text = element_text(size=15),
        axis.title.x = element_text(size = 15), axis.title.y = element_text(size = 15)) +
  labs(x = 'Network size', y = 'Proportion infected') +
  labs(fill = 'Network size') +
  stat_summary(fun=mean, geom="point", size=3)
```







